Bird Density, with Edge ML

### 2019-12-06 report/paper.tex
Added some images

\section{Hardware}
The first revision of the hardware is finished and we have connected to the microcontroller. The physical hardware is shown in Figure \ref{hardware} while the schematic is shown in Figure \ref{sch1} and \ref{sch2}. We got a PCB manufactued overseas ans placed all the SMD components onto it.

\begin{figure}[H]
\centering
\includegraphics[scale=0.15]{../birdEar/img/be.jpg}
\caption{Hardware}
\label{hardware}
\end{figure}

>>>>

\section{Hardware}
The first revision of the hardware is finished and we have connected to the microcontroller, we have blinked on of the LEDs but have not implemented any sampling or the neural network. The physical hardware is shown in Figure \ref{hardware} while the schematic is shown in Figure \ref{sch1} and \ref{sch2}. We got a PCB manufactued overseas ans placed all the SMD components onto it.

\begin{figure}[H]
\centering
\includegraphics[scale=0.07]{img/E04A0175.JPG}
\caption{Hardware}
\label{hardware}
\end{figure}
